---
title: "XYZ Firm"
author: "George.B"
date: "2022-12-16"
output:
  pdf_document: default
  html_document: default
---

# Summary

* What was the United State of America's GDP from 2001 to 2018.
* Which States in the United State has the Highest GDP from 2001 to 2018.
* List the Counties in the United State with the Highest GDP from 2005 to 2018

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(dplyr)
library(janitor)
library(skimr)
library(lubridate)
library(tidyr)
library(ggplot2)
library(colorspace)
library(here)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
library(readr)
GDP_by_County <- read_csv("C:/Users/pc/Desktop/my project raw file/usa county with the highest gdp/GDP_by_County.csv")
View(GDP_by_County)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
USA_gdp <- GDP_by_County %>% 
  group_by(Year) %>%
  drop_na() %>% 
  summarise(total_gdp_yearly=sum(GDP_in_dollars))
print(USA_gdp)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = USA_gdp)+
  geom_smooth(mapping = aes(x=Year,y=total_gdp_yearly))+
  geom_point(mapping = aes(x=Year, y=total_gdp_yearly, fill=Year))+
  labs(title = "Year by Year GDP", subtitle = "USA GDP from 2001 to 2018")
```

* The chart above shows the year to year Gross Domestic Profit(GDP) for United State America.
* The USA Economy grew from $13,230,272,271,000 in **2001** to $18,244,233,031,000 in 2018,but the the GDP dropped in 2008 and 2009
 


```{r message=FALSE, warning=FALSE, include=FALSE}
gdp_par_state <- GDP_by_County %>% 
  group_by(Year, State) %>%
  drop_na() %>% 
  summarise(total_gdp_yearly=sum(GDP_in_dollars))
view(gdp_par_state)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
gdp_par_state2 <- gdp_par_state %>% 
  group_by(total_gdp_yearly,Year,State) %>% 
  summarise(state_with_highest_gdp=max(total_gdp_yearly)) %>% 
  tail(20)
print(gdp_par_state2)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
ggplot(data = gdp_par_state2, aes(x=Year,y=state_with_highest_gdp, fill=Year))+
  geom_col(position = "dodge")+
  facet_wrap(~State)+
  labs(title = "GDP by States", subtitle = "States with the Highest GDPs from 2001 to 2018")
```

* This chart shows USA states with the highest Gross Domestic Profit (GDP) from 2001 to 2018.
* California has the highest GDP more than any other state in USA with a GDP of $1,705,688,782,000 in 2001 to $2,723,055,904,000. California GDP grew with over 1 trillion dollars in 12 years.
* The State of Texas comes second wth a GDP of $1,652,917,964,000 in 2017 and $!,723,693,999,000 in 2018.




```{r message=FALSE, warning=FALSE, include=FALSE}
gdp_by_county <- GDP_by_County %>% 
  group_by(Year,State,County) %>% 
  drop_na() %>% 
  summarise(county_gdp=sum(GDP_in_dollars))
view(gdp_by_county)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
gdp_by_county2 <- gdp_by_county %>% 
  group_by(county_gdp,Year,State,County) %>% 
  drop_na() %>% 
  summarise(counties_with_highest_gdp=max(county_gdp)) %>% 
  tail(20)
print(gdp_by_county2)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
ggplot(data = gdp_by_county2, aes(x=Year,y=counties_with_highest_gdp, fill=State))+
  geom_col(position = "dodge")+
  facet_wrap(~County)+
  labs(title = "GDP by Counties", subtitle = "The counties with the Highest GDPs from 2005 to in 2018")
```

* This chart shows GDP by counties the highest GDP in each State in USA.
* The County of Los Angeles has the highest GDP among other County from 2005 to 2018 with a GDP of $550,159,000,000 in 2005 and $710,893,000,000 in 2018.
* While the County of New York came in second every time from with a GDP of $544,566,000,000 in 2012 and $600,244,000,000 in 2018.







